\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom




%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\title{Important Thoughts}
\author{Marco Brianti}
\date{A.Y. 2018/2019}

\begin{document}
	\large{

\maketitle

\section*{Comments during and after the Presentation}

\begin{itemize}
	\item Re-adjust the law of motion for cash. It must be right! You forget on interest payments or net debt position.
	\item Since my problem is going to be linear then you can think about presenting shocks to be linear as well...
	\item Do not use same $g(\cdot)$ for slide 2 and the model.
	\item Third derivative condition is not so obvious. Provide a fast intuition!
	\item Ryan is pushing to do a FAVAR to be more elastic in the exercise. You need to ask to Peter!
	\item How to link reduced-form residual to the identification problem? Improve that part!
	\item Key question. Is it necessary to have $\delta$ to be the same in both? Answer seems to be YES! Need to understand why...
	\item You need to show the uniqueness of $\delta$.
	\item How should I interpret $\delta$ in a theoretical setting?
\end{itemize}


}
\end{document}

